### 2015-03-04 slides/mascot-tree/mascot-tree.tikz.tex
Working on slides.

%% Coordinates of nodes.
\draw [black!00,line width=10.0pt] (6.340,-0.500) -- (6.340,11.000);
\draw [black!00,line width=10.0pt] (13.400,-0.500) -- (13.400,11.000);
\draw [draw=none] (10.97, 9.75) node[circle, minimum width=10pt, draw=none, inner sep=0pt, path picture={\draw[red] (path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);}] {};
\draw [draw=none] (6.34, 10.4) node[circle, minimum width=10pt, draw=none, inner sep=0pt, path picture={\draw[red] (path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);}] {};
\draw [draw=none] (13.4, 7.15) node[circle, minimum width=10pt, draw=none, inner sep=0pt, path picture={\draw[red] (path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);}] {};
\coordinate (n0) at (0.000,7.947);
\coordinate (n1) at (6.330,10.400);
\coordinate (n1p) at (0.000,10.400);
\coordinate (n2) at (0.487,5.493);
\coordinate (n2p) at (0.000,5.493);
\coordinate (n3) at (10.956,9.750);
\coordinate (n3p) at (0.487,9.750);
\coordinate (n4) at (2.435,1.237);
\coordinate (n4p) at (0.487,1.237);
\coordinate (n5) at (2.800,2.148);
\coordinate (n5p) at (2.435,2.148);
\coordinate (n6) at (3.409,2.996);
\coordinate (n6p) at (2.800,2.996);
\coordinate (n7) at (4.504,4.042);
\coordinate (n7p) at (3.409,4.042);
\coordinate (n8) at (4.626,5.484);
\coordinate (n8p) at (4.504,5.484);
\coordinate (n9) at (6.330,7.109);
\coordinate (n9p) at (4.626,7.109);
\coordinate (n10) at (9.739,7.719);
\coordinate (n10p) at (6.330,7.719);
\coordinate (n11) at (12.661,8.287);
\coordinate (n11p) at (9.739,8.287);
\coordinate (n12) at (13.391,8.775);
\coordinate (n12p) at (12.661,8.775);
\coordinate (n13) at (14.365,9.100);
\coordinate (n13p) at (13.391,9.100);
\coordinate (n14) at (14.365,8.450);
\coordinate (n14p) at (13.391,8.450);
\coordinate (n15) at (14.365,7.800);
\coordinate (n15p) at (12.661,7.800);
\coordinate (n16) at (13.391,7.150);
\coordinate (n16p) at (9.739,7.150);
\coordinate (n17) at (14.365,6.500);
\coordinate (n17p) at (6.330,6.500);
\coordinate (n18) at (6.330,3.859);
\coordinate (n18p) at (4.626,3.859);
\coordinate (n19) at (11.443,4.469);
\coordinate (n19p) at (6.330,4.469);
\coordinate (n20) at (13.391,5.038);
\coordinate (n20p) at (11.443,5.038);
\coordinate (n21) at (14.122,5.525);
\coordinate (n21p) at (13.391,5.525);
\coordinate (n22) at (14.365,5.850);
\coordinate (n22p) at (14.122,5.850);
\coordinate (n23) at (14.365,5.200);
\coordinate (n23p) at (14.122,5.200);
\coordinate (n24) at (14.365,4.550);
\coordinate (n24p) at (13.391,4.550);
\coordinate (n25) at (14.365,3.900);
\coordinate (n25p) at (11.443,3.900);
\coordinate (n26) at (14.365,3.250);
\coordinate (n26p) at (6.330,3.250);
\coordinate (n27) at (14.365,2.600);
\coordinate (n27p) at (4.504,2.600);
\coordinate (n28) at (14.365,1.950);
\coordinate (n28p) at (3.409,1.950);
\coordinate (n29) at (14.365,1.300);
\coordinate (n29p) at (2.800,1.300);
\coordinate (n30) at (6.330,0.325);
\coordinate (n30p) at (2.435,0.325);
\coordinate (n31) at (14.365,0.650);
\coordinate (n31p) at (6.330,0.650);
\coordinate (n32) at (14.365,0.000);
\coordinate (n32p) at (6.330,0.000);

>>>>

%% Coordinates of nodes.
\draw [black!00,line width=10.0pt] (6.340,-0.500) -- (6.340,11.000);
\draw [black!00,line width=10.0pt] (13.400,-0.500) -- (13.400,11.000);
\draw [draw=none] (10.97, 9.75) node[circle, minimum width=10pt, draw=none, inner sep=0pt, path picture={\draw[red] (path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);}] {};
\draw [draw=none] (7.08, 10.4) node[circle, minimum width=10pt, draw=none, inner sep=0pt, path picture={\draw[red] (path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);}] {};
\draw [draw=none] (13.17, 7.15) node[circle, minimum width=10pt, draw=none, inner sep=0pt, path picture={\draw[red] (path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);}] {};
\coordinate (n0) at (0.000,7.947);
\coordinate (n1) at (7.061,10.400);
\coordinate (n1p) at (0.000,10.400);
\coordinate (n2) at (0.487,5.493);
\coordinate (n2p) at (0.000,5.493);
\coordinate (n3) at (10.956,9.750);
\coordinate (n3p) at (0.487,9.750);
\coordinate (n4) at (2.435,1.237);
\coordinate (n4p) at (0.487,1.237);
\coordinate (n5) at (2.800,2.148);
\coordinate (n5p) at (2.435,2.148);
\coordinate (n6) at (3.409,2.996);
\coordinate (n6p) at (2.800,2.996);
\coordinate (n7) at (4.504,4.042);
\coordinate (n7p) at (3.409,4.042);
\coordinate (n8) at (4.626,5.484);
\coordinate (n8p) at (4.504,5.484);
\coordinate (n9) at (6.574,7.109);
\coordinate (n9p) at (4.626,7.109);
\coordinate (n10) at (9.739,7.719);
\coordinate (n10p) at (6.574,7.719);
\coordinate (n11) at (12.661,8.287);
\coordinate (n11p) at (9.739,8.287);
\coordinate (n12) at (13.635,8.775);
\coordinate (n12p) at (12.661,8.775);
\coordinate (n13) at (14.365,9.100);
\coordinate (n13p) at (13.635,9.100);
\coordinate (n14) at (14.365,8.450);
\coordinate (n14p) at (13.635,8.450);
\coordinate (n15) at (14.365,7.800);
\coordinate (n15p) at (12.661,7.800);
\coordinate (n16) at (13.148,7.150);
\coordinate (n16p) at (9.739,7.150);
\coordinate (n17) at (14.365,6.500);
\coordinate (n17p) at (6.574,6.500);
\coordinate (n18) at (6.087,3.859);
\coordinate (n18p) at (4.626,3.859);
\coordinate (n19) at (11.443,4.469);
\coordinate (n19p) at (6.087,4.469);
\coordinate (n20) at (13.391,5.038);
\coordinate (n20p) at (11.443,5.038);
\coordinate (n21) at (14.122,5.525);
\coordinate (n21p) at (13.391,5.525);
\coordinate (n22) at (14.365,5.850);
\coordinate (n22p) at (14.122,5.850);
\coordinate (n23) at (14.365,5.200);
\coordinate (n23p) at (14.122,5.200);
\coordinate (n24) at (14.365,4.550);
\coordinate (n24p) at (13.391,4.550);
\coordinate (n25) at (14.365,3.900);
\coordinate (n25p) at (11.443,3.900);
\coordinate (n26) at (14.365,3.250);
\coordinate (n26p) at (6.087,3.250);
\coordinate (n27) at (14.365,2.600);
\coordinate (n27p) at (4.504,2.600);
\coordinate (n28) at (14.365,1.950);
\coordinate (n28p) at (3.409,1.950);
\coordinate (n29) at (14.365,1.300);
\coordinate (n29p) at (2.800,1.300);
\coordinate (n30) at (6.330,0.325);
\coordinate (n30p) at (2.435,0.325);
\coordinate (n31) at (14.365,0.650);
\coordinate (n31p) at (6.330,0.650);
\coordinate (n32) at (14.365,0.000);
\coordinate (n32p) at (6.330,0.000);
